### 2018-07-16 experiments.tex
get ready for issre
PLDI 13 to FPF benchmark change

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.02\textwidth]{jscurve}
        \caption{Discovery curves for SpiderMonkey 1.6 faults}
        \label{jscurves}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.02\textwidth]{gcccurve}
        \caption{Discovery curves for GCC 4.3.0 wrong-code faults}
        \label{gcccurves}
    \end{subfigure}
    \caption{Discovery curves compared to best curves from PLDI 2013}
\end{figure*}

@@

Our primary experiments are based on subjects used in the only previous study of compiler fuzzer taming \cite{PLDI13}.  Of the three data sets examined in that paper, this paper considers two:  faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.  GCC 4.3.0 crash faults were essentially perfectly localized by previous approaches.  In fact, on examination, only two of the 11 crash bugs are not distinguished by simply examining the crash message.  Faults that produce a crash are also likely to be much easier to debug than semantic problems such as all of the GCC wrong code bugs and most of the JavaScript faults --- e.g., following a dynamic slice might well suffice.

@@

Our mutants were produced using the tool written by Jamie Andrews \cite{mutant}.  Andrews' tool applies only four operators: statement deletion, conditional negation, operator replacement, and constant replacement, chosen as a small set that still produces good results for C code.  Experiments were performed on a MacBook Pro with 16GB RAM and dual-core 3.1GHz Intel Core i7; GCC executed on a VirtualBox-hosted Ubuntu 11.04.  For GCC, some test cases from the 2013 PLDI paper no longer failed, presumably due to unknown differences in execution environment, OS, or memory layout. Discarding these reduced the set of test cases from 1,275 to 1,117 and the number of distinct faults to 27 rather than 35.  For SpiderMonkey, all 1,749 test cases from the PLDI 2013 data failed in the new environment, representing 28 distinct faults.

@@

APFD results are useful summaries, but the curve itself is also worth examining, since (1) long sequences of tests with no new faults may discourage users more than an overall less effective but steadily climbing curve with few ``plateaus'' as we call these uninformative sequences of tests and (2) a good early curve is important to developers.  The mutant repair curve climbs very rapidly in the early portion, with perfect discovery for the first 12 faults. The largest plateau is 5 tests without a new fault, ignoring the long period after the 31st test.  In fact, a plateau at the end of the curve is not problematic.  Assuming that few users will examine more than 50 test cases without fixing some faults, the user may give up after seeing 10 or more tests without a new fault based on the mutant repair curve, and in fact lose nothing by doing so.  The PLDI 2013 curve, in contrast, has a plateau of size 17 after the 17th fault.  If we assume a user stops examining tests after a size 10 or greater plateau, the user will only see 17 faults using the PLDI 2013 metric, vs. 19 with our metric.  Stopping at a plateau of size 6 produces the same results.

@@

In order to check our results statistically, we sliced the PLDI 13 tests into 20 randomly selected equal-sized (as much as possible) distinct subsets.  The repair metric had a mean APFD (89.23\%) for these subsets that was 2.85\% better than the mean APFD for the PLDI 13 metric (86.76\%), over sets of $\sim 10$ faults. The result was statistically significant ($p < 0.05$ by Wilcoxon test).   Median repair APFD was 90.05\%, vs. 84.75\% for PLDI 13's best metric.

@@

Table \ref{bothtable} only includes 8 of the 28 SpiderMonkey faults.  This is due to a problem with the data set:  producing ground truth patches for a large application, in the sense of finding a minimal, clearly fault-fixing code change that can be back-ported to the original code is difficult \cite{PLDI13}.  While we believe the 28 faults identified in the PLDI 2013 data set are correct, it is very difficult to produce a valid patch of version 1.6 that captures the fix for most of these faults.  In some cases the final commit that caused tests to stop failing appeared to only be the end of a complex series of changes that converged on a correct fix.  In other cases, the code was modified so extensively before the fix that identifying ``the incorrect part'' of the original code seemed to owe more to guesswork than certainty.  The evaluation of localization therefore only examines the 8 faults for which we could be reasonably certain that the patch to 1.6 was correct and characterized the fault in question accurately.  In no case was the patch equivalent to one of the mutants (the smallest patch modified two statements).

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{comparegcc}
  \caption{APFD values for GCC suite slices}
  \label{comparegcc}
\end{figure}%

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best PLDI 2013 curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve (first 15 tests) is worse compared to the PLDI 2013 curve, but still has a maximum gap of only 2 redundant tests vs. 4 for PLDI 13.  Over all, again the curve is better than the best PLDI 13 curve at 60\% of all points.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage only yields 16 faults over 31 tests.

@@

Slicing the GCC tests into 20 random equal-sized test subsets and comparing with function and line coverage metrics (Figure \ref{comparegcc}) we find that differences in APFD values are statistically significant between our metric and both PLDI 13 metrics, by Wilcoxon test, with $p < 0.0005$, and the mean APFD improvement --- even for only 55 tests, exposing only 6-11 faults (mean of 7.75 faults) --- is more than 3.8\% better than either PLDI 13 metric.

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users simply do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection in their PLDI work.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, since trying multiple metrics is impractical: a user has to examine each curve.  \comment{It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.}  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work; our improvements over any single ``reasonable'' method applied to both problems would be considerably larger (for instance, using the most obvious basis, line coverage, we see more than 17\% improvement).  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD from best-previous method is around 3\%, and statistically significant.

@@

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply.   Whether sampling mutants \cite{RahulISSRE} is applicable is less clear.  Even if the FPF curve remains the same, a critical mutant for localization might be omitted.  We performed some limited experiments, and found that for a few sample sizes ranging from 13\% of mutants to 50\% of mutants or using only some mutation operators (with the exception of operator-replacement-only), APFD was always better than PLDI 13 best.   However, the improvement in some cases was \emph{much} smaller than for the full set, and varied considerably (in some cases it was up to 2\% better than our full results).  Fault localization results were much worse, however (with relative rankings preserved) for both our techniques and MUSE/MUSEUM.  \comment{Finally, guided sampling may provide good fuzzer taming (if not fault localization):  compute vectors over a small constant-sized \cite{RahulISSRE} sample of mutants, then report highly distinct failing tests.  Other metrics, such as coverage-based comparisons, could provide hints as to likely distinct tests (and thus mutants covered by them) to focus on first.  These are likely to be different faults.  After repairing some of these, choose mutants to evaluate that are covered by multiple tests with few or no repairing mutants (since such tests are the ones most likely to be distinct but not yet identified).  Such an approach could be quite cost-effective, requiring only a relatively small number of mutant evaluations before providing useful results.}

>>>>

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{jscurve}
        \caption{Discovery curves for SpiderMonkey 1.6 faults}
        \label{jscurves}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{gcccurve}
        \caption{Discovery curves for GCC 4.3.0 wrong-code faults}
        \label{gcccurves}
    \end{subfigure}
    \caption{Discovery curves compared to best curves from Chen et. al PLDI 2013 data (FPF benchmark)}
\end{figure*}

@@

Our primary experiments are based on subjects used in the only previous study of compiler fuzzer taming (from Chen et al.'s PLDI 2013 paper \cite{PLDI13}), which we hereafter refer to as the FPF benchmark.  Of the three data sets examined in that paper, this paper considers two:  faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.  GCC 4.3.0 crash faults were essentially perfectly localized by previous approaches.  In fact, on examination, only two of the 11 crash bugs are not distinguished by simply examining the crash message.  Faults that produce a crash are also likely to be much easier to debug than semantic problems such as all of the GCC wrong code bugs and most of the JavaScript faults --- e.g., following a dynamic slice might well suffice.

@@

Our mutants were produced using the tool written by Jamie Andrews \cite{mutant}.  Andrews' tool applies only four operators: statement deletion, conditional negation, operator replacement, and constant replacement, chosen as a small set that still produces good results for C code.  Experiments were performed on a MacBook Pro with 16GB RAM and dual-core 3.1GHz Intel Core i7; GCC executed on a VirtualBox-hosted Ubuntu 11.04.  For GCC, some test cases from the FPF set no longer failed, presumably due to unknown differences in execution environment, OS, or memory layout. Discarding these reduced the set of test cases from 1,275 to 1,117 and the number of distinct faults to 27 rather than 35.  For SpiderMonkey, all 1,749 test cases from the FPF benchmark failed in the new environment, representing 28 distinct faults.

@@

APFD results are useful summaries, but the curve itself is also worth examining, since (1) long sequences of tests with no new faults may discourage users more than an overall less effective but steadily climbing curve with few ``plateaus'' as we call these uninformative sequences of tests and (2) a good early curve is important to developers.  The mutant repair curve climbs very rapidly in the early portion, with perfect discovery for the first 12 faults. The largest plateau is 5 tests without a new fault, ignoring the long period after the 31st test.  In fact, a plateau at the end of the curve is not problematic.  Assuming that few users will examine more than 50 test cases without fixing some faults, the user may give up after seeing 10 or more tests without a new fault based on the mutant repair curve, and in fact lose nothing by doing so.  The best FPF benchmark curve, in contrast, has a plateau of size 17 after the 17th fault.  If we assume a user stops examining tests after a size 10 or greater plateau, the user will only see 17 faults using the best benchmark metric, vs. 19 with our metric.  Stopping at a plateau of size 6 produces the same results.

@@

In order to check our results statistically, we sliced the FPF benchmark tests into 20 randomly selected equal-sized (as much as possible) distinct subsets.  The repair metric had a mean APFD (89.23\%) for these subsets that was 2.85\% better than the mean APFD for the best benchmark metric (86.76\%), over sets of $\sim 10$ faults. The result was statistically significant ($p < 0.05$ by Wilcoxon test).   Median repair APFD was 90.05\%, vs. 84.75\% for the best benchmark metric.

@@

Table \ref{bothtable} only includes 8 of the 28 SpiderMonkey faults.  This is due to a problem with the data set:  producing ground truth patches for a large application, in the sense of finding a minimal, clearly fault-fixing code change that can be back-ported to the original code is difficult \cite{PLDI13}.  While we believe the 28 faults identified in the FPF benchmark data are correct, it is very difficult to produce a valid patch of version 1.6 that captures the fix for most of these faults.  In some cases the final commit that caused tests to stop failing appeared to only be the end of a complex series of changes that converged on a correct fix.  In other cases, the code was modified so extensively before the fix that identifying ``the incorrect part'' of the original code seemed to owe more to guesswork than certainty.  The evaluation of localization therefore only examines the 8 faults for which we could be reasonably certain that the patch to 1.6 was correct and characterized the fault in question accurately.  In no case was the patch equivalent to one of the mutants (the smallest patch modified two statements).

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{comparegcc}
  \caption{APFD values for GCC suite slices}
  \label{comparegcc}
\end{figure}%

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best benchmark curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve (first 15 tests) is worse compared to the benchmark curve, but still has a maximum gap of only 2 redundant tests vs. 4 for the benchmark.  Over all, again the curve is better than the best benchmark curve at 60\% of all points.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage only yields 16 faults over 31 tests.

@@

Slicing the GCC tests into 20 random equal-sized test subsets and comparing with function and line coverage metrics (Figure \ref{comparegcc}) we find that differences in APFD values are statistically significant between our metric and both benchmark metrics, by Wilcoxon test, with $p < 0.0005$, and the mean APFD improvement --- even for only 55 tests, exposing only 6-11 faults (mean of 7.75 faults) --- is more than 3.8\% better than either benchmark metric.

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users simply do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, since trying multiple metrics is impractical: a user has to examine each curve.  \comment{It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.}  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work; our improvements over any single ``reasonable'' method applied to both problems would be considerably larger (for instance, using the most obvious basis, line coverage, we see more than 17\% improvement).  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD from best-previous method is around 3\%, and statistically significant.

@@

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply.   Whether sampling mutants \cite{RahulISSRE} is applicable is less clear.  Even if the FPF curve remains the same, a critical mutant for localization might be omitted.  We performed some limited experiments, and found that for a few sample sizes ranging from 13\% of mutants to 50\% of mutants or using only some mutation operators (with the exception of operator-replacement-only), APFD was always better than benchmark set's best metric.   However, the improvement in some cases was \emph{much} smaller than for the full set, and varied considerably (in some cases it was up to 2\% better than our full results).  Fault localization results were much worse, however (with relative rankings preserved) for both our techniques and MUSE/MUSEUM.  \comment{Finally, guided sampling may provide good fuzzer taming (if not fault localization):  compute vectors over a small constant-sized \cite{RahulISSRE} sample of mutants, then report highly distinct failing tests.  Other metrics, such as coverage-based comparisons, could provide hints as to likely distinct tests (and thus mutants covered by them) to focus on first.  These are likely to be different faults.  After repairing some of these, choose mutants to evaluate that are covered by multiple tests with few or no repairing mutants (since such tests are the ones most likely to be distinct but not yet identified).  Such an approach could be quite cost-effective, requiring only a relatively small number of mutant evaluations before providing useful results.}
